%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\break\cvsection{Project}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {} % Job title
    {Sayone Technologies - IPC Website} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        {IPC is the largest Pentecostal denomination in India with more than 7000 churches worldwide, controlled by the General Council. There are huge number of users in the IPC community, This Web Application helps to manage the data of  the user efficienly.}
        \item {\textbf{Technologies:} Django, Django Templating, Postgresql, Jquery, Ajax}
      \end{cvitems}
    }

  \cventry
    {} % Job title
    {Sayone Technologies - Datafloq Forum} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        {Datafloq offers information, insights and opportunities to drive innovation with big data, blockchain, artificial intelligence and other emerging technologies. Datafloq Forum is where you allows visitors to communicate with each other by posting questions and answering them (Similar to stackoverflow).}
        \item {\textbf{Technologies:} Django, Askbot, Django Templating, Mysql, Jquery, Ajax}
      \end{cvitems}
    }
  
  \cventry
    {} % Job title
    {Selectrooms Backend} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        {SelectRooms is a hotel search with an extensive price comparison. The prices shown come from numerous hotels and booking websites. Selectroom backend fetches data from various providers and offers exclusive hotel deals at highly discounted rates}
        \item {\textbf{Technologies:} Django, Flask, Mysql, Redis, Huey, Celery}
      \end{cvitems}
    }
    
  \cventry
    {} % Job title
    {Fetchr - Middleware} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        {Middleware acts as a backend service for Fetchr's mobile and web applications. This allows the customer to create logistics order and help them to schedule the order based on the timeslot they choose.}
        \item {\textbf{Technologies:} Django, PostgreSQL, Pytest, Jenkins}
      \end{cvitems}
    }

\cventry
    {} % Job title
    {Fetchr - 3PL Service} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        {The Couriers Microservice exists to provide Fetchr with the ability to create Orders on External Parties/Platforms and to track the status of such orders Created on external platforms}
        \item {\textbf{Technologies:} Flask, PostgreSQL, Pytest, Jenkins}
      \end{cvitems}
}
\cventry
    {} % Job title
    {Fetchr - Customer Management} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        {Customer Management helps the customer support to manage the Fetchr's customer profile
        such as their phone number and email}
        \item {\textbf{Technologies:} Django Rest Framework, PostgreSQL, Pytest, Ansible, Bootstrap }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
